Lazy Stack Properties

### 2020-04-28 LazyStackProperties.tex
Added version of integrity that corresponds better to the coq development

>>>>

    \paragraph{Observable Integrity Closer to the Development}

      In the interest of matching the coq development, here is an alternate formulation of observable integrity
      that talks just about subroutines and is just phrased as operating on traces. Assume that there is just
      one stack, \(S\). In this version, a system enjoys {\it observable stack integrity} if for all
      \(\overline{T} = \dots T_1 T_2 \dots T_3 \overline{T}_4\) such that \(T_1 = M_1,\sigma_1,S\), 
      \(T_2 = M_2,\sigma_2,S\), \(T_3 = M_3,\sigma_3,S\), and \(T_1\) and \(T_3\) bracket a call,
      there is a safe state \(T_3' = M_3',\sigma_3,S\) where:
      \[M_3'(K) =
      \begin{cases}
        M_1(K) & \text{if } \mathit{contour}(\sigma_1,S)(K) = \mathtt{A} \text{ and }
                 \mathit{contour}(\sigma_2,S)(K) = \mathtt{IL} \\
        M_3(K) & \text{else} \\
      \end{cases}\]

      And the observable trace \(\mathit{behav}(T_3' \overline{T}_4')\) is prefixed by
      \(\mathit{behave}(T_3 \overline{T}_4)\).

      This variant of the property ought to be combined with a coroutine equivalent, and it captures the
      same intuition as the {\sc Safe} execution version, though it would need to be proven that the two are
      equivalent.
